---
title: "R Notebook"
output: html_notebook
---

Database Example


docker run --mount type=bind,source=./mysql.properties,target=/etc/trino/catalog/mysql.properties -p 8080:8080 --name trino trinodb/trino

docker run --mount type=bind,src=./mysql.properties,dst=/etc/trino/catalog/mysql.properties -p 8080:8080 --name trino trinodb/trino

# this worked
docker run --mount type=bind,source="//c/Users/david/OneDrive/SW Dev Fun/Data_Mesh/mysql.properties",target=/etc/trino/catalog/mysql.properties -p 8080:8080 --name trino trinodb/trino


docker run --mount type=bind,source=mysql.properties,target=\etc\trino\catalog\mysql.properties -p 8080:8080 --name trino trinodb/trino

docker exec -it trino bash

docker exec -it <container_process> trino


```{r}
library(DBI)
library(RMariaDB)
library(tidyverse)
```


```{r}
con <- dbConnect(RMariaDB::MariaDB(), dbname="default_1", user="coker", password="coker", host="localhost", group="my-db")

dbListTables(con)
# dbClearResult()

res4 <- dbGetQuery(con, "SELECT * FROM mtcars WHERE cyl = 4")
#dbFetch(res)
res4

dbGetQuery(
  con,
  "SELECT COUNT(*) FROM mtcars WHERE cyl = ?",
  params = list(1:8)
)

res6 <- dbGetQuery(con, "SELECT * FROM mtcars WHERE cyl = 6")
#dbFetch(res)
res6

# disconnect from DataBase
dbDisconnect(con)
```



```{r}
con <- dbConnect(RMariaDB::MariaDB(), dbname="default_1", user="coker", password="coker", host="localhost", group="my-db")

mtcars2 <- tbl(con,"mtcars")


summary <- mtcars2 %>%
  group_by(cyl) %>%
  summarise(mpg=mean(mpg,na.rm=TRUE)) %>%
  arrange(desc(mpg))

summary %>% show_query()

summary %>% collect()
# disconnect from DataBase
dbDisconnect(con)
```


# TRINO

https://github.com/prestodb/RPresto

```{r eval=FALSE, include=FALSE}
library(RPresto)
```


```{r eval=FALSE, include=FALSE}

# httr::set_config(httr::add_headers("X-Presto-User"=Sys.getenv("USER")) )

pcon <- dbConnect(
  RPresto::Presto(),
  use.trino.headers=TRUE, # addresses uniqueness from core prestodb
  host='http://localhost',
  port=8080,
  user='coker',
  password='***empty***',
  # password='password',
  catalog='mysql',
  schema='default_1'
)

dbGetQuery(pcon, "SELECT count(*) FROM mtcars")

res <- dbSendQuery(pcon, "SELECT * FROM mtcars WHERE cyl = 4")
dbFetch(res)

```


# using basic JDBC Driver
https://stackoverflow.com/questions/57898334/how-do-i-use-rpresto-to-connect-to-a-database-using-https

library(rJava)
library(RJDBC)
new_presto_driver <- JDBC(classPath = "path/to/driver/referenced/above.jar"))

presto_jdbc <- dbConnect(
  new_presto_driver,
  user = "dlucas",
  password = "password",
  url = "jdbc:presto://presto.###.com:PORT_NUMBER/CATALOG",
  SSL = true
)

presto_jdbc <- dbConnect(new_presto_driver1,
                         user="coker",
                         password="***empty***",
                         url="jdbc:trino://localhost/default_1:8080",
                         SSL=FALSE)
                         
                         

```{r}
# if needed
Sys.setenv(JAVA_HOME='C:\\Program Files\\Java\\jre1.8.0_321') 
library(rJava)
library(RJDBC)

# this works!!
new_presto_driver1 <- JDBC(driverClass="io.trino.jdbc.TrinoDriver",
                           classPath = "C:\\Users\\david\\OneDrive\\SW Dev Fun\\Data_Mesh\\trino-jdbc-361.jar")

# This works!!!
presto_jdbc <- dbConnect(new_presto_driver1,
                         user="coker",
                         password="***empty***",
                         url="jdbc:trino://localhost:8080",
                         SSL=FALSE)

dbGetQuery(presto_jdbc, "SHOW CATALOGS")
dbGetQuery(presto_jdbc, "SHOW SCHEMAS FROM mysql")
dbGetQuery(presto_jdbc, "SHOW TABLES FROM mysql.default_1")
dbGetQuery(presto_jdbc, "SELECT count(*) FROM mysql.default_1.mtcars")
dbGetQuery(presto_jdbc, "SHOW COLUMNS FROM mysql.default_1.mtcars")
dbGetQuery(presto_jdbc, "DESCRIBE mysql.default_1.mtcars")
dbGetQuery(presto_jdbc, "SELECT * from mysql.default_1.mtcars WHERE cyl=6")

res <- dbSendQuery(presto_jdbc, "SELECT * FROM mysql.default_1.mtcars WHERE cyl = 4")
dbFetch(res)

```


install.package("devtools")
devtools::install_github("gadenbuie/lorem")
https://github.com/gadenbuie/lorem

ipsum_items <- replicate(5, lorem::ipsum_words(5))
cat(paste("-", ipsum_items), sep = "\n")


```{r Ipsum Lorem Generator}
# install.package("devtools")
# devtools::install_github("gadenbuie/lorem")
library(lorem)



```

```{r GUID Generator}
library(uuid)



```

```{r}
library (lubridate)

```


```{r Generate PIRs}
# generate N paragraphs averaging PW words each
N <- 50 # Number of PIRs to generate
PW <- 20 # number of words in a paragaph for ipsum lorem
PIR_Comments <- ipsum(N,avg_words_per_sentence = PW)
TW <- 5 # number of words for a single sentence item
PIR_Title <- replicate(N, lorem::ipsum_words(TW))
PIR_GUID <- UUIDgenerate(use.time=FALSE,n=N)
EW <- 10 # number of words
EEI <- replicate(N, lorem::ipsum_words(EW))
NW <- 4 # number of words
NIPF <- replicate(N,lorem::ipsum_words(NW))

CLASSIFICATION <- c("Sample U", "Sample S", "Sample TS")
RELEASABILITY <- c("//", "// NOFORN", "// REL FEYES", "// REL ROK", "// REL NATO" )
CCMD_List <- c("SOCOM", "SOUTHCOM","CENTCOM","INDOPACOM","STRATCOM",
               "NORTHCOM","EUCOM","AFRICOM","CYBERCOM","TRANSCOM")
CCMD_Comp <- c("AF","NAVY","ARMY",
               "SOF","SPACE","MARINES")
#### Need to add CMD to the PIRs
PIR_CCMD <- sample(CCMD_List,N,replace=TRUE)

# Phasing 
Phase <- c(0,1,2,4,5)
PIR_Phase <- rep(Phase[1],N)

# generate dates for records
start_date <- as.POSIXct("2015-01-15")
PIR_Date <- start_date
for(i in 1:N) PIR_Date[i] <- start_date + hours(i*5)

PIR <- data.frame(
  GUID = PIR_GUID,
  Phase = PIR_Phase,
  CCMD = PIR_CCMD,
  Date_Time = PIR_Date,
  Title = PIR_Title,
  Description = PIR_Comments,
  EEI = EEI,
  NIPF = NIPF,
  Classification = sample(CLASSIFICATION, N, replace=TRUE),
  Releasability = sample(RELEASABILITY, N, replace=TRUE)
)

con <- dbConnect(RMariaDB::MariaDB(), dbname="default_1", user="coker", password="coker", host="localhost", group="my-db")
dbWriteTable(con,"PIR",PIR, overwrite=TRUE)
dbDisconnect(con)

```


```{r Generate RFC}
library(stringi) # used to generate BE#'s
NR <- 400 # number of RFCs to generate 
N_Users <- 100
N_Groups <- 7

# Random list of KIQ GUIDs
NK <- 50
KIQ_GUID <- UUIDgenerate(use.time=FALSE,n=NK)

# Generate a list of dates to chose from randomly
start_date <- as.POSIXct("2016-03-15")
R_Date <- start_date
for(i in 1:NR) R_Date[i] <- start_date + hours(i*5)

# CCMD List
CCMD_List <- c("SOCOM", "SOUTHCOM","CENTCOM","INDOPACOM","STRATCOM",
               "NORTHCOM","EUCOM","AFRICOM","CYBERCOM","TRANSCOM")
CCMD_Comp <- c("AF","NAVY","ARMY",
               "SOF","SPACE","MARINES")
R_Type <- c("AD-HOC", "STANDING")
RFC_TL <- c("ROUTINE", "IMMEDIATE","UNKNOWN")
WF_List <- c("DRAFT","PENDING","APPROVED","REJECTED","PAUSED")
Priority <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)

RFC_GUID <- UUIDgenerate(use.time=FALSE,n=NR)
Created_Date_Time <- R_Date[as.integer(runif(NR,1,NR+1))]
Created_By <- sample.int(N_Users, NR, replace=TRUE) # user ID, integer
LastUpdated_Date_Time <- Created_Date_Time + hours(as.integer( runif(1,0,80)))
LastUpdated_By <- sample.int(N_Users, NR, replace=TRUE) # user ID, integer
Workflow_Status <- sample(WF_List,NR,replace=TRUE) 
RFC_Title <- replicate(NR, lorem::ipsum_words(TW))
RFC_Comments <- ipsum(NR,avg_words_per_sentence = PW)
# build linkage to PIR
RFC_PIR_GUID <- sample(PIR_GUID,NR,replace=TRUE) # Randomly select one of the PIRs
# get the following from the associated PIR
pirguid_index <- match(RFC_PIR_GUID,PIR$GUID)

CCMD <- sample(CCMD_List,NR,replace=TRUE)
CCMD_Component <- sample(CCMD_Comp,NR,replace=TRUE) 
Request_Type <- sample(R_Type,NR,replace=TRUE) # AD-HOC, STANDING
RFC_Timeline <- sample(RFC_TL,NR,replace=TRUE) # ROUTINE, IMMEDIATE
RFC_Begin <- sample(R_Date,NR, replace=TRUE) 
RFC_End <- RFC_Begin + days(as.integer( runif(1,30,120)))
RFC_LTV <- RFC_End + days(as.integer( runif(1,10,30)))
RFC_Comments <- ipsum(NR,avg_words_per_sentence = PW)
RFC_rand <- ipsum(NR,avg_words_per_sentence = PW)
pRFC_Research <- ipsum(NR,avg_words_per_sentence = 10) # Links
RFC_rand <- ipsum(NR,avg_words_per_sentence = PW)
rPOC <- sample.int(N_Users, NR, replace=TRUE)  # user ID, integer
KIQ_ID <- sample(KIQ_GUID, NR, replace=TRUE) 
groupID <- sample.int(N_Groups, NR, replace=TRUE) # integer
MIDB_ID <- do.call(paste0, c("BE", Map(stri_rand_strings, n=NR, length=c(5, 4, 1),
            pattern = c('[A-Z]', '[0-9]', '[A-Z]'))))

# Create Coordinates for each RFC
min_lat <- 30
max_lat <- 45
min_lon <- -140
max_lon <- -120
RFC_Lat <- runif(NR,min_lat,max_lat)
RFC_Lon <- runif(NR,min_lon,max_lon)



RFC <- data.frame(
  GUID = RFC_GUID,
  Created_Date_Time = Created_Date_Time,
  Created_By = Created_By, # user ID, integer
  LastUpdated_Date_Time = LastUpdated_Date_Time,
  LastUpdated_By = LastUpdated_By, # user ID, integer
  Workflow_Status = Workflow_Status,
  Title = RFC_Title,
  Description = RFC_Comments,
  PIR = RFC_PIR_GUID,
  Combatant_Command = CCMD,
  Combatant_Command_Component = CCMD_Component,
  requestType = Request_Type, # AD-HOC, STANDING
  collectionTimeline = RFC_Timeline, # ROUTINE, IMMEDIATE
  collectionStartDate = RFC_Begin,
  collectionStopDate = RFC_End,
  collectionLastTimeofValue = RFC_LTV,
  background = RFC_Comments,
  justification = RFC_rand,
  previousCollectionResearch = pRFC_Research, # Links
  summary = RFC_rand,
  responsiblePointofContactId = rPOC, # User ID, integer
  keyIntelligenceQuestionId = KIQ_ID, # GUID
  groupId = groupID, # integer
  TargetID = MIDB_ID,
  lon = RFC_Lon,
  lat = RFC_Lat,
  Priority = sample(Priority, NR, replace=TRUE),
  Classification = PIR$Classification[pirguid_index],
  Releasability = PIR$Releasability[pirguid_index]
)

library(ggplot2)
library(maps)

usa <- map_data("usa")

ggplot() + 
  geom_map(data=usa,map=usa, aes(x=long,y=lat,map_id=region), fill="orange",color="black") +
  geom_point(data=RFC, aes(x=lon,y=lat), color="red", size=1)

con <- dbConnect(RMariaDB::MariaDB(), dbname="default_1", user="coker", password="coker", host="localhost", group="my-db")
dbWriteTable(con,"rfc",RFC,overwrite=TRUE)
dbDisconnect(con)


```



```{r Generate GEOINT CR}

NCR <- 1000
CR_List <- c("MTI","Surveillance","Reconnaissance")

CR_GUID <- UUIDgenerate(use.time=FALSE,n=NCR)
Created_Date_Time <- sample(R_Date, NCR, replace=TRUE) 
Created_By <- sample.int(N_Users,NCR, replace=TRUE) # user ID, integer
LastUpdated_Date_Time <- Created_Date_Time + hours(as.integer( runif(1,0,80)))
LastUpdated_By <- sample.int(N_Users,NCR, replace=TRUE) # user ID, integer
Workflow_Status <- sample(WF_List, NCR, replace= TRUE) 
CR_Title <- replicate(NCR, lorem::ipsum_words(TW))
CR_Comments <- ipsum(NCR,avg_words_per_sentence = PW)
# pick a random RFC GUID to associate with
# Randomly select one of the RFCs for each CR
CR_RFC_GUID <- sample(RFC$GUID, NCR, replace=TRUE)
# get the following from the associated RFC 
rfcguid_index <- match(CR_RFC_GUID,RFC$GUID)

CR_CCMD <- CCMD[rfcguid_index]
CR_CCMD_Component <- CCMD_Component[rfcguid_index]
CR_Type <- sample(CR_List, NCR, replace = TRUE) 
CR_Target <- MIDB_ID[rfcguid_index]
CR_Timeline <- RFC_Timeline[rfcguid_index] # ROUTINE, IMMEDIATE
CR_Begin <- RFC_Begin[rfcguid_index]
CR_End <- RFC_End[rfcguid_index]

CR_Comments <- ipsum(NCR,avg_words_per_sentence = PW)
CR_rand <- ipsum(NCR,avg_words_per_sentence = PW)
CR_rand <- ipsum(NCR,avg_words_per_sentence = PW)
CRPOC <- sample.int(N_Users, NCR, replace=TRUE)  # user ID, integer
CRgroupID <- as.integer(runif(NCR,1,7)) # integer


# generate coordinates for the CRs tied to the RFC coords
CR_Lon <- RFC_Lon[rfcguid_index] + runif(NCR,-0.1,0.1)
CR_Lat <- RFC_Lat[rfcguid_index] + runif(NCR,-0.1,0.1)

CR <- data.frame(
  GUID = CR_GUID,
  Created_Date_Time = Created_Date_Time,
  Created_By = Created_By, # user ID, integer
  LastUpdated_Date_Time = LastUpdated_Date_Time,
  LastUpdated_By = LastUpdated_By, # user ID, integer
  Workflow_Status = Workflow_Status,
  Title = CR_Title,
  Description = CR_Comments,
  RFC = CR_RFC_GUID,
  Combatant_Command = CR_CCMD,
  Combatant_Command_Component = CR_CCMD_Component,
  collectType = CR_Type, # AD-HOC, STANDING
  collectionTimeline = CR_Timeline, # ROUTINE, IMMEDIATE
  collectionStartDate = CR_Begin,
  collectionStopDate = CR_End,
  #collectionLastTimeofValue = RFC_LTV,
  background = CR_Comments,
  justification = CR_rand,
  summary = CR_rand,
  responsiblePointofContactId = CRPOC, # User ID, integer
  groupId = CRgroupID, # integer
  TargetID = CR_Target,
  lon = CR_Lon,
  lat = CR_Lat,
  Priority = RFC$Priority[rfcguid_index],
  Classification = RFC$Classification[rfcguid_index],
  Releasability = RFC$Releasability[rfcguid_index]
)


usa <- map_data("usa")

ggplot() + 
  geom_map(data=usa,map=usa, aes(x=long,y=lat,map_id=region), fill="orange",color="black") +
  geom_point(data=RFC, aes(x=lon,y=lat), color="red", size=4) +
    geom_point(data=CR, aes(x=lon,y=lat), color="blue", size=1)


con <- dbConnect(RMariaDB::MariaDB(), dbname="default_1", user="coker", password="coker", host="localhost", group="my-db")
dbWriteTable(con,"cr",CR,overwrite=TRUE)
dbDisconnect(con)

```


```{r Joins}

rfc_pir <- left_join(RFC, PIR, by = c("PIR" = "GUID"), suffix = c(".rfc", ".pir"))

cr_rfc <- left_join(CR, RFC, by = c("RFC" = "GUID"), suffix = c(".cr", ".rfc"))

ggplot() + 
  geom_map(data=usa,map=usa, aes(x=long,y=lat,map_id=region), fill="orange",color="black") +
  geom_point(data=cr_rfc, aes(x=lon.rfc,y=lat.rfc), color="red", size=4) +
    geom_point(data=cr_rfc, aes(x=lon.cr,y=lat.cr), color="blue", size=1)

cr_rfc_pir <- left_join(cr_rfc, PIR, by =c("RFC" = "GUID"))


con <- dbConnect(RMariaDB::MariaDB(), dbname="default_1", user="coker", password="coker", host="localhost", group="my-db")
dbWriteTable(con,"crrfcpir",cr_rfc_pir,overwrite=TRUE)
dbDisconnect(con)

dd <- tbl(con,"crrfcpir")
summary(dd)
summary <- dd %>% filter(Combatant_Command.rfc == "CENTCOM") %>%
  filter(Workflow_Status.cr == "APPROVED")
summary %>% show_query()
summary %>% collect()
dd <- tbl(con)
summary <- dd %>% left_join(RFC, PIR, by = c("PIR" = "GUID"), suffix = c(".rfc", ".pir"))


cr_rfc_pir %>% filter(Combatant_Command.rfc == "CENTCOM") %>%
  filter(Workflow_Status.cr == "APPROVED")
```

```{r Create Graph}
#  https://kateto.net/netscix2016.hthml
# https://rforpoliticalscience.com/2020/10/15/create-network-graphs-with-igraph-and-ggnet2-packages-in-r/
library(igraph)
library(ggraph) 

PIR$Combatant_Command <- PIR$CCMD
vertex_pir <- PIR %>% select(GUID,Title,Combatant_Command) %>%
  mutate(TYPE="PIR",COLOR="gray50",SIZE=4)
vertex_rfc <- RFC %>% select(GUID,Title,Combatant_Command) %>% 
  mutate(TYPE="RFC",COLOR="tomato",SIZE=6)
vertex_cr <-  CR %>% select(GUID,Title,Combatant_Command) %>% 
  mutate(TYPE="CR",COLOR="gold",SIZE=4)
vertex <- rbind(vertex_pir, vertex_rfc, vertex_cr)

edges_rfc_pir <- rfc_pir %>% 
  select(GUID, PIR) %>% 
  mutate(G1=GUID, G2= PIR, GUID=NULL, PIR=NULL,TYPE1="RFC", TYPE2="PIR")
edges_cr_rfc <- cr_rfc %>% 
  select(GUID,RFC) %>% 
  mutate(G1=GUID, G2= RFC, GUID=NULL, RFC=NULL,TYPE1="CR",TYPE2="RFC")
edges <- rbind(edges_rfc_pir,edges_cr_rfc)

net <- graph_from_data_frame(d=edges, vertices=vertex, direct="TRUE")
net <- delete.vertices(net,degree(net)<1) # remove stand alone nodes
# net <- delete.vertices(net,V(net)$TYPE != "PIR")
# trim down to a manageable set
net <- delete.vertices(net,V(net)$Combatant_Command!= "CENTCOM")

#clp <- cluster_optimal(net)

colrs <- c("gray50", "tomato", "gold")
V(net)$color <- V(net)$COLOR
V(net)$label <- V(net)$TYPE
#plot(clp,net, edge.color="orange", vertex.size=6, edge.arrow.size=0,
#     vertex.label.cex=1, vertex.label.color="black", edge.curved=0.2,
 #    layout=layout_with_fr(net))

plot(net, edge.color="orange", vertex.size=6, edge.arrow.size=0,
     vertex.label.cex=1, vertex.label.color="black", edge.curved=0.2,
     layout=layout_with_fr(net))

# get stats on pir nodes and rfc nodes
net <- graph_from_data_frame(d=edges, vertices=vertex, direct="TRUE")
net <- delete.vertices(net,degree(net)<1) # remove stand alone nodes
pp <- V(net)$TYPE == "PIR"
pirdeg <- degree(net)
pirdeg <- pirdeg[pp]
hist(pirdeg)

pr <- V(net)$TYPE == "RFC"
rfcdeg <- degree(net)
rfcdeg <- rfcdeg[pr]
hist(rfcdeg)


# legend(x=-1.5, y=-1.1, c("PIR","RFC","CR"))

# 
# net <- cr_rfc %>% 
#   filter(Combatant_Command.rfc == "CENTCOM") %>% 
#   filter(Workflow_Status.cr == "APPROVED") %>%
#   select(GUID,RFC) %>% 
#   graph_from_data_frame(,directed="FALSE")
# 
# # , vertices=as.data.frame[cr_rfc$Title.rfc,cr_rfc$Title.cr])
# 
# plot(net, vertex.color="green", edge.color="orange", vertex.size=6, 
#      vertex.label.cex=0.4, vertex.label.color="black")


# 
# ggraph(net) + 
#   geom_edge_link() +
#   geom_node_point()

```

